Results

### 2025-06-16 notebooks/000_data.qmd
update

@@

@@

>>>>

### Parker Solar Probe

@@

The parameters are:

- 'psp_fld_l2_mag_RTN_4_Sa_per_Cyc' (B in RTN, 0.25s resolution)
- 'psp_swp_spi_sf00_L3_DENS' (Ion density, regular resolution)
- 'psp_swp_spi_af00_L3_DENS' (Ion density, burst resolution)
- 'psp_swp_spi_sf00_L3_VEL_RTN_SUN' (velocity in RTN in Sun's frame, regular resolution)
- 'psp_swp_spi_af00_L3_VEL_RTN_SUN' (velocity in RTN in Sun's frame, burst resolution)
- 'psp_swp_spi_sf00_L3_VEL_RTN' (velocity in RTN in spacecraft frame, regular resolution, you need this to calculate current sheet thickness)
- 'psp_swp_spi_af00_L3_VEL_RTN' (velocity in RTN in spacecraft frame, burst resolution, you need this to calculate current sheet thickness)
- 'Tp_spani_b' (Ion parallel and perpendicular ion temperature, regular resolution. Blue (first element in array): parallel, Red: perp)
- 'Tp_spanib_b' (Ion parallel and perpendicular ion temperature, burst resolution. Blue (first element in array): parallel, Red: perp)

@@

### SOLO

"cda/SOLO_L2_MAG-RTN-NORMAL-1-MINUTE/B_RTN",
"cda/SOLO_L2_SWA-PAS-GRND-MOM/N",
"cda/SOLO_L2_SWA-PAS-GRND-MOM/V_RTN",
"cda/SOLO_L2_SWA-PAS-GRND-MOM/T",

### STEREO

"cda/STA_L2_PLA_1DMAX_1MIN/proton_number_density",
"cda/STA_L2_PLA_1DMAX_1MIN/proton_bulk_speed",
"cda/STA_L2_PLA_1DMAX_1MIN/proton_n_s_flow_angle_inst",
"cda/STA_L2_PLA_1DMAX_1MIN/proton_e_w_flow_angle_inst",
"cda/STA_L2_PLA_1DMAX_1MIN/proton_Vr_RTN",

### 2025-06-16 notebooks/00_index.qmd
update

@@

```{julia}
using Speasy
using SPEDAS: tnorm_combine, tplot, DataSet
using DimensionalData
using CairoMakie
# using GLMakie
using Statistics
using PartialFunctions
using Unitful
using Beforerr: _theme_legend, easy_save
using SPEDAS.SpaceDataModel: set, extend, @set
include("../src/psp_temp.jl")
include("../src/meta.jl")

@@

```{julia}
# along time get the temperature from anisotropic temperature
function tTemp(x; dims=Ti)
    return mean.(eachslice(x; dims))
end

mva_transform((V, B), tmin, tmax; tb_min=tmin, tb_max=tmax) = mva(V(tmin, tmax), B(tb_min, tb_max))
make_mva_transform(tb_min, tb_max) = mva_transform$(; tb_min, tb_max)

j_transform((V, B), tmin, tmax) = current_density(B(tmin, tmax), V(tmin, tmax))
```

@@

```{julia}
psp_B = set(tnorm_combine ∘ PSP.B_1MIN; ylabel=𝒀.B, labels=𝑳.B_RTN)
psp_V = set(PSP.V; ylabel=𝒀.V, labels=𝑳.V_RTN)
psp_n = set(PSP.n_spi; ylabel=𝒀.n, yscale=identity)

@@

```{julia}
wind_B = set(tnorm_combine ∘ Wind.B_GSE_1MIN; ylabel=𝒀.B, labels=𝑳.B_XYZ)
wind_V = replace_outliers! ∘ set(Wind.V_GSE_K0; ylabel=𝒀.V, labels=𝑳.V_XYZ)

tvars_wind = [wind_B, set(Wind.n_p_K0; ylabel=𝒀.n), wind_V]
tvars_wind_all = [
    wind_B,
    set(Wind.n; ylabel=𝒀.n),
    wind_V,
    set(Wind.T; ylabel=𝒀.T)
]
```

```{julia}
using CairoMakie
CairoMakie.activate!()
```

@@

```{julia}
update_theme!(; Lines=(linewidth=1, alpha=0.9), figure_padding=(0, 0, 0, 15))

@@

    _tmask! = get_themis_tmask(tmin_wind, tmax_wind)

@@

    f = Figure(; size=(800, 450))
    plots = tplot(f[1, 1], tvars_psp[1:3], tmin_psp, tmax_psp; legend)
    add_labels!(f[1, 1]; labels, open="(a.", padding)
    tplot(f[1, 2], tvars_wind[1:3], tmin_wind, tmax_wind; legend)
    add_labels!(f[1, 2]; labels, open="(b.", padding)
    # tplot(f[1, 3], _tmask! .∘ tvars_themis[1:3], tmin_wind, tmax_wind; legend)
    # add_labels!(f[1, 3]; labels, open="(c.")
    easy_save("overview-$enc")

>>>>

```{julia}
using DimensionalData
Tp = PSP.read_proton_temperature(7:8)
Te = PSP.read_electron_temperature()

tselect(A, t) = A[Ti(Near(t))]
function tselect(A, t, δt)
    tmp = @views A[Ti((t - δt) .. (t + δt))]
    length(tmp) == 0 ? missing : tmp[Ti(Near(t))]
end

deunit(x::Quantity, u) = NoUnits(x / u)
deunit(x, u) = x

function add_temp_anisotropy!(df, Tp_para, Tp_perp, Te_para, Te_perp, dt=Minute(1))
    @rtransform! df begin
        :Tp_para = deunit(tselect(Tp_para, :time, dt), u"eV")
        :Tp_perp = deunit(tselect(Tp_perp, :time, dt), u"eV")
        :Te_para = deunit(tselect(Te_para, :time, dt), u"eV")
        :Te_perp = deunit(tselect(Te_perp, :time, dt), u"eV")
    end
end

add_temp_anisotropy!(df, Tp, Te, args...) =
    add_temp_anisotropy!(df, Tp.para, Tp.perp, Te.para, Te.perp, args...)

add_temp_anisotropy!(psp_df, Tp, Te)
compute_anisotropy_params!(psp_df, :ion => (:Tp_para, :Tp_perp), :electron => (:Te_para, :Te_perp))
```

@@

```{julia}
using Speasy
using SPEDAS: tnorm_combine, tplot, DataSet
using DimensionalData
using CairoMakie
# using GLMakie
using Statistics
using PartialFunctions
using Unitful
using Beforerr: _theme_legend, easy_save
using SPEDAS.SpaceDataModel: set, extend, @set

@@

```{julia}
mva_transform((V, B), tmin, tmax; tb_min=tmin, tb_max=tmax) = mva(V(tmin, tmax), B(tb_min, tb_max))
```

@@

```{julia}
psp_B = set(tnorm_combine ∘ PSP.B_1MIN; ylabel=𝒀.B, labels=𝑳.B_RTN)
psp_V = set(PSP.V; ylabel=𝒀.V, labels=𝑳.V_RTN)
psp_n = PSP.n_spi

@@

```{julia}
wind_B = set(tnorm_combine ∘ Wind.B_GSE_1MIN; ylabel=𝒀.B, labels=𝑳.B_XYZ)
wind_V = replace_outliers! ∘ set(Wind.V_GSE_K0; ylabel=𝒀.V, labels=𝑳.V_XYZ)
wind_n = set(Wind.n_p_K0; ylabel=𝒀.n, yscale=identity)

tvars_wind = [wind_B, wind_n, wind_V]
tvars_wind_all = [
    wind_B,
    set(Wind.n; ylabel=𝒀.n),
    wind_V,
    set(Wind.T; ylabel=𝒀.T)
]
```

@@

Alfvén ratio over time

```{julia}
using StatsBase
using DimensionalData
using NaNStatistics

function get_vl_ratio_ts(df)
    vl_ratio_ts1 = DimArray(df.v_l_ratio, Ti(df.time))
    vl_ratio_ts2 = DimArray(df.v_l_ratio_Λ, Ti(df.time))
    gfunc = x -> floor(x, Hour(4))
    vl_ratio_ts = hcat(
        nanmedian.(disallowmissing.(groupby(vl_ratio_ts1, Ti => gfunc))),
        nanmedian.(disallowmissing.(filter.(!ismissing, groupby(vl_ratio_ts2, Ti => gfunc))))
    )
    set_meta!(vl_ratio_ts; ylabel=L"R_{VB}", labels=["Isotropy", "Anisotropy"])
    return vl_ratio_ts
end
```

```{julia}
update_theme!(; Lines=(linewidth=1, alpha=0.9), figure_padding=(1, 1, 1, 15))

# for enc in 7:9
plot_vl_ratio = true

function modify_faxs_base!(faxs)
    B_ax = faxs.axes[1]
    B_ax.ylabel[] = 𝒀.B
    n_ax = faxs.axes[2]
    n_ax.yscale[] = identity
    n_ax.ylabel[] = 𝒀.n
    V_ax = faxs.axes[3]
    V_ax.ylabel[] = 𝒀.V
end

function modify_faxs_vl!(faxs)
    ylims!(faxs.axes[end-1], 0.09, 0.85)
    faxs.axes[4].ylabel[] = "T (eV)"
    β_ax = faxs.axes[6]
    β_ax.yscale[] = log10
    β_ax.ylabel[] = "β"
    ylims!(β_ax, 8e-2, 4e1)
end

@@

@@

    f = Figure(; size=(800, 600))

    tvars_psp = (psp_B, psp_n, psp_V)
    tvars_wind = (wind_B, wind_n, wind_V)

    fname = "overview-$enc"

    if plot_vl_ratio
        fname = "overview-vl-$enc"

        B = set_meta!(PSP.B_1MIN(tmin_psp, tmax_psp); labels=𝑳.B_RTN)
        V = set_meta!(psp_V(tmin_psp, tmax_psp); labels=𝑳.V_RTN)
        n = PSP.n_spi(tmin_psp, tmax_psp)
        T = PSP.pTemp(tmin_psp, tmax_psp; add_unit=false)

        B_mag = tnorm(B)
        β = Discontinuity.plasma_beta.(tsync(T, n, B_mag)...)

        T = rebuild(T; metadata=(; labels=[L"T_p"]))

        psp_v_l_ratio_ts = get_vl_ratio_ts(psp_df)
        tvars_psp = (tnorm_combine(B), n, V, [T, Tp, Te], psp_v_l_ratio_ts, β)

        Wind_Tp2 = Wind.pTemp_T2(tmin_wind, tmax_wind)
        Wind_Te2 = Wind.eTemp_T2(tmin_wind, tmax_wind)
        add_temp_anisotropy!(wind_df, Wind_Tp2, Wind_Te2, Minute(2))
        compute_anisotropy_params!(wind_df, :ion => (:Tp_para, :Tp_perp), :electron => (:Te_para, :Te_perp))

        B = Wind.B_GSE_1MIN(tmin_wind, tmax_wind)
        n = Wind.n_p_K0(tmin_wind, tmax_wind) |> tsort
        T = rebuild(Wind.T_p_PLSP(tmin_wind, tmax_wind) |> tsort; metadata=(; labels=[L"T_p"]))
        B_mag = tnorm(B)
        β = Discontinuity.plasma_beta.(tsync(T, n, B_mag)...)

        wind_v_l_ratio_ts = get_vl_ratio_ts(wind_df)
        tvars_wind = (tvars_wind..., [T, Wind.Temp_ani[1:2]...], wind_v_l_ratio_ts, β)
    end

    faxs = tplot(f[1, 1], tvars_psp, tmin_psp, tmax_psp; legend)
    modify_faxs_base!(faxs)
    plot_vl_ratio && modify_faxs_vl!(faxs)
    add_labels!(f[1, 1]; labels, open="(a.", padding)
    faxs = tplot(f[1, 2], tvars_wind, tmin_wind, tmax_wind; legend)
    modify_faxs_base!(faxs)
    plot_vl_ratio && modify_faxs_vl!(faxs)
    add_labels!(f[1, 2]; labels, open="(b.", padding)
    # _tmask! = get_themis_tmask(tmin_wind, tmax_wind)
    # tplot(f[1, 3], _tmask! .∘ tvars_themis[1:3], tmin_wind, tmax_wind; legend)
    # add_labels!(f[1, 3]; labels, open="(c.")
    easy_save(fname; formats=(:pdf,))
    display(f)
